Investigate relations in incomplete datasets to inform imputation model

### 2020-02-18 3.Thesis/inspect_incomplete_data.Rmd
added functionalities to apply lm to all variables and missingness indicators

```{r}
# plot this for each missingness indicator
dat %>%
  map(~{ggplot(data=dat, aes(x = age, fill = is.na(.x))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = names(.),
    breaks = c("FALSE", "TRUE"),
    labels = c("Observed", "Missing"),
    values = c("#006CC2", "#B61A51")
  )})

# only the name of the legend does not work. maybe look into pmap?
```

>>>>

```{r}
# plot this for each missingness indicator
vars <- names(dat)
vars %>%
  map(~{ggplot(data=dat, aes(x = age, fill = is.na(.data[[.x]]))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = .x,
    breaks = c("FALSE", "TRUE"),
    labels = c("observed", "missing"),
    values = c("#006CC2", "#B61A51")
  )})

# now for all vars as outcome
```
# Part 2B: Apply to all variables as outcome

This works for age now, with all missingness indicators. But not yet for other variables as outcome.

```{r}
# apply map to our own problem
interc_only <- dat %>% lm(age ~ 1, data = .)
vars <- names(dat)
#dat %>% map(~class(.x)=="numeric")
#dat[ ,map_lgl(dat, is.numeric)]
#dat %>% map(~is.numeric(.x)) select_if(x, is.numeric)
cont_vars <- dat %>% select_if(is.numeric) %>% names()
#walk(cont_vars,~ walk(vars, ~ print(paste(.x, .y, sep = "-")),.y=.x))
#test <- map(cont_vars, function(x) map(vars, function(y) c(x,y)))
#test <- map(cont_vars, function(x) map(vars, function(y) c(dat[1,x],is.na(dat[1,y]))))
test <- map(cont_vars, function(x) map(vars, function(y) lm(dat[,x]~is.na(dat[,y]))))

# this works for the lm, but not yet for the intercep-only model
#all_interc_only <- cont_vars %>% map(~lm(dat[,.x] ~ 1))
# test2 <- map(cont_vars, function(x) map(vars, function(y) lm(dat[,x]~is.na(dat[,y])) %>% anova(interc_only[[x]], .)))
# map(test, function(x) map(interc_only, function(y) anova(y,x)))
test <- map(cont_vars, function(x) map(vars, function(y) {anova(lm(dat[,x]~1), lm(dat[,x]~is.na(dat[,y])))}))
